Response to the defense feedback

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret input and record the memory access for each execution. Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment. For one type of event (e.g., function $a$ executes), we use $p$ to denote the probability of the event. Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$. Therefore, the times of the same observation for each event should satisfy the binomial distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

@@

According to chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. In this chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent. We use the above method to test if any two leakage sites are independent for each leakage point. We combine them into a leakage and calculate the total amount of the leakage.
\section{Design}
In this section, we explain the design of \ctool{}.
We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

>>>>

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret input and record the memory access for each execution. Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment. For one type of event (e.g., function $a$ executes), we use $p$ to denote the probability of the event. Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$. Therefore, the times of the same observation for each event should satisfy the binomial distribution. After that, we can use the chi-squared test to examine whether the two leakage sites are independent.

@@

According to chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are likely to independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. In this chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent. We use the above method to test if any two leakage sites are independent for each leakage point. If any two leakages are independent, we combine them into one leakage and calculate the total amount of the leaked information.
\section{Design}
In this section, we explain the design of \ctool{}.
We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
